NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-27 paper/application.tex
update layout of the paper
update tasks
update section 5

\section{Put it All Together}

\label{sec:caseStudy}

In this section, we utilizes the perturbation based analysis
to illustrate how the proposed system can be used
to diagnose the model behavior, study the model's attention mechanism.

@@

% \subsection{Is Attention All You Need?}

>>>>

\section{Application Story}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
In this section, we utilizes the perturbation based analysis to illustrate how the proposed system can help the domain experts making sense of attention mechanism and assess the behavior of the model.

\subsection{Is the Prediction Stable?}
\shusen{difference in sensitivity among entail netural and contradict relationships}

@@

\subsection{What Does It Take to Change the Prediction?}

\subsection{Is Attention All You Need?}

### 2018-03-27 paper/sentence.tex
update section 5

\subsection{Sentence View}
\label{sec:sentence}
To start an exploration cycle, the experts need to examine the premise and hypothesis sentence the current example.
As illustrated in Fig.~\ref{fig:sentenceView}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
%
To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces nous and verb by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
%
When perturbation is applied to either of the sentences, the replaced words are highlight in blue (see Fig~\ref{fig:modelPipeline}(e) ) to indicate the modification to the original sentence.
%
In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis, provided there is only one perturbation per sentence pair (i.e., we use original premise if hypothesis is perturbed, or use original hypothesis if premise is perturbed).
%%% sentence perturbation %%%%
In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
In addition, the user can type any sentences or modified existing text in the (c) and (d) to accommodate customized input when expert want to conduct quick experiment or when the automatic perturbation does not meet expectations.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{sentenceView}
 \caption{
Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the original text is highlight in blue, as illustrated in (e)
In (a), \emph{Predict} and \emph{Predict All}, each corresponds to predict the current displayed sentence pairs, or predict all combinations of perturbed premise and hypothesis.
In (b), previous explored original sentence are stored in the dropdown list that allow the user to revisit previous examined sentence.
 }
\label{fig:sentenceView}
\end{figure}

>>>>

\subsection{Sentence View}
\label{sec:sentence}
% Once an exploration cycle started, the experts need to examine the premise and hypothesis sentence the current example.
As illustrated in Fig.~\ref{fig:sentenceView}, the sentence view shows the premise and hypothesis sentence in (c) and (d).
%
To facilitate the analysis task (\textbf{T1}), we employ an automate sentence perturbation scheme that replaces \emph{nouns} and \emph{verbs} by their synonymous in the wordNet~\cite{Miller1995} (the standard lexical database for NLP applications).
%
When the perturbation is applied to either of the sentences, the replaced words are highlighted in blue (see Fig~\ref{fig:modelPipeline}(e) ) to signal the modification made to the original sentence.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.95\linewidth]{sentenceView}
 \vspace{-2mm}
 \caption{
 Sentence view shows the premise (c) and the hypothesis (d) sentence pair. The word that replaces the word in the original text is highlighted in blue (e).
 The \emph{Predict} and \emph{Predict All} controls (a) correspond to predicting the currently displayed sentence pairs and predicting all combinations of perturbed premise and hypothesis, respectively.
 Previous explored original sentence are stored in the dropdown list (d) that allow the user to revisit previous examined sentence.
}
\label{fig:sentenceView}
\end{figure}

At the top left of the view, the two controls \emph{Predict} and \emph{Predict All} (a) correspond to predicting the currently displayed sentence pairs and predict all combinations of perturbed premise and hypothesis, respectively.
%
To avoid the situation where both sentences are perturbed, we ensure that only one perturbation per sentence pair (i.e., we use original premise if the hypothesis is perturbed, or use original hypothesis if the premise is perturbed).
%%% sentence perturbation %%%%
The previous explored original sentences are stored in the dropdown list (see Fig.~\ref{fig:sentenceView}(b)) that allow the user to revisit previous examined sentence.
Also, the user can type any sentences or modified existing text in text areas (Fig.~\ref{fig:sentenceView}(c)(d)) to accommodate customized input when expert want to conduct a quick experiment or when the automatic perturbation is not sufficient.
